Roster Review (Generic)

### 2019-06-04 rosterReview_generic.Rmd
Standardize import of new projections

```{r}
force <- TRUE
force_all <- FALSE
batter_file <- NULL
pitcher_file <- NULL

rosters <- load_players_with_projections(force, force_all, batter_file, pitcher_file)
```

@@

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Utleys",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Utleys",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters %>% 
  filter(grepl("process|Dorn",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Cain|Price|Romo|Trout|Whitley|Claudio",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```

>>>>

```{r}
force <- TRUE
force_all <- FALSE
batter_file <- "temp/FanGraphs Leaderboard.csv"
pitcher_file <- "temp/FanGraphs Leaderboard (1).csv"

if (force_all && (batter_file %>% is.null() || pitcher_file %>% is.null())) {
  stop("Need projection files to force a recalc")
} else {
  rosters <- load_players_with_projections(force, 
                                           force_all, 
                                           batter_file, 
                                           pitcher_file)
}

```

@@

```{r}
# TODO find way to wrap these three views into one
rosters %>% 
  filter(grepl("Plouffe|Deez",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  arrange(zar %>% desc) %>% 
  View()
  # mutate(zar = janitor::round_half_up(zar)) %>% 
  # write_csv("data/tradeReview_20190423.csv")

rosters %>% 
  filter(grepl("Plouffe|Deez",team)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type)), width=.2) +
  coord_flip() -> tv

@@

rosters %>% 
  filter(grepl("Dorn|Plouffe",team)) %>% 
  select(team, manager, name_full, display_position, zar) %>% 
  filter(grepl("Puig|Yonny Chir",name_full)) %>% 
  group_by(team) %>% 
  summarize(zar = sum(zar))
```
